Comprehensive study of the global phase diagram in the triangular $J$-$K$-$\Gamma$ model

### 2020-11-11 paper/paper.tex
Paper 2020-08-25 18:20

\title{Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model}

@@

\begin{abstract}
The celebrated Kitaev honeycomb model provides an analytically tractable example with an exact quantum spin liquid ground state. While in real materials, other types of interactions besides the Kitaev coupling are present and these models can also be generalized to a triangular lattice. Here, we study the classical and quantum Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice using the classical Monte Carlo and exact diagonalization. We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit. Near the antiferromagetic Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism. Also, the order-by-disorder mechanism selects the ferromagnetic ordered states as the ground state out of the degenerate classical states for the pure $\Gamma$ models. Around the positive $\Gamma$ point, due to the interplay of the Heisenberg, Kiatev and $\Gamma$ interactions, we find a possible quantum spin liquid in a noticeable region with a continuum in spin excitations.
\end{abstract}

@@

In this paper, we comprehensively study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses. We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations. In the HK limit ($\Gamma=0$), there are five classical phases: one FM, two stripe, one $120^{\circ}$ N\'{e}el and its dual phases. For the pure AFM Kitaev model, although the system has highly degenerate classical GSs composed of the stripe and nematic states, the order-by-disorder mechanism caused by quantum fluctuations makes the system select the stripe state to be the GS. When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases. With the aid of classical analysis, we determine the spin configuration for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders. On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate. For the possible QSL phase, based on the investigation of the spin excitation spectrum, we find that the GS is probably a gapped $Z_{2}$ QSL.

@@

The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details). We find nine magnetically ordered phases and a possible QSL phase. The nine ordered magnetic phases consist of three stripe phases (dubbed as stripe-A, strip-B and stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}), three ferromagnetic phases (dubbed as FM-A, FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}), one 120$^\circ$ N\'{e}el phase, one dual N\'{e}el phase and one modulated stripe phase. In the followings, we will discuss the details on the natures of these phases and the corresponding phase transitions.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/HKModel.pdf}
    \caption{\label{fig:HKModel}(Color online) Phase diagram in the HK limit ($\Gamma=0$). The double-arrow lines are the representative lines that connect the points exactly related by the FST.}
\end{figure}
Let's first discuss the the HK limit for $\Gamma=0$. As with the previous study~\cite{KaiLi2015}, we find five quantum phases (see Fig.~\ref{fig:HKModel}). For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state (denoted as FM-A) for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively. As mentioned in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions. Thus, by virtue of the FST, we can identify other two magnetically ordered phases. For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$. Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state (denoted as stripe-A) of $\bm{S}$. Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$, and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$. Moreover, as indicated in Fig.~\ref{fig:HKModel}, the transition points $\beta=0.23\pi$ and $0.64\pi$ can also be well mapped to the transition points $\beta=1.90\pi$ and $1.82\pi$ through the FST. The isolated transition point $\beta=\pi$ is also consistent with the FST, as it is mapped to itself under the FST.

For the phase near the AFM Kitaev point ($J=\Gamma=0$, $K=1$), which is between $\beta=1.90\pi$ and $0.23\pi$,  the points in this phase are still mapped to those in the same phase under the FST, so we can not identify its magnetic properties by the FST, and it was supposed to be a magnetically disordered phase in our previous study~\cite{KaiLi2015}. However, as shown in Fig.~\ref{fig:StructureFactors}(a), when we check the SSF in this phase, we find that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase. To find out, we further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters. We find that there are two types of degenerate classical GSs, one of which has the stripe order and the other is the nematic state, since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details). When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order. As shown in Fig.~\ref{fig:StructureFactors}(i), the peaks of SSF of the classical stripe orders are also consistent with the result calculated from ED [see Fig.~\ref{fig:StructureFactors}(a)]. Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-B. Moreover, every stripe order in this phase (see Appendix~\ref{apx:DegeneratedStates} for details) can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.

Next, we will discuss the effects of the $\Gamma$ term on the phase diagram. A natural conjecture is that the phases in the HK limit ($\Gamma=0$) would extend to a larger region in the global phase diagram of the $J$-$K$-$\Gamma$ model. Our ED results do show that the stripe-A phase can extend to a large region from $\Gamma>0$ to $\Gamma<0$, which is consistent with the previous classical results~\cite{PhysRevB.92.165108}. The region of the dual N\'{e}el phase that was dubbed as a dual-$Z_{2}$ vortex crystal phase in Ref.~\onlinecite{PhysRevB.92.165108} is also consistent with the classical results. However, we find that an infinitesimal $\Gamma$ interaction can make the FM-A phase and the stripe-B phase unstable, so these two phases are actually phase boundaries in the global phase diagram. On the other hand, although the the 120$^\circ$ N\'{e}el phase can also extend to a certain region, its area in the phase diagram is much smaller than the classical results~\cite{PhysRevB.92.165108}. Besides these phases that already exist in the HK limit, there are five other new phases according to our ED calculations. Since the SSF is a key physical quantity to reveal the nature of each quantum phases, especially the spin configuration of the ordered phases, we will discuss the properties of the phases with $\Gamma\neq0$ in detail according to the SSFs.

In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e. $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively. Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i). Thus, this further confirms that the stripe-A phase extents to a large region in the phase diagram. In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ in a new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.

@@

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the classical analyses by using the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, there are also several noncollinear magnetic orders energetically degenerate with the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). However, according to our ED calculations, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states. This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) strip-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL. The green dashed lines marks the first BZ of the triangular lattice. (i) Characteristic wave vectors for the FM and stipe phases. See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
\end{figure}

According to the above analysis, we find that, unlike the case for the honeycomb lattice, the Kitaev interactions on the triangular lattice do not give rise to QSL states, so the quantum phase diagram is similar to its classical counterpart~\cite{PhysRevB.92.165108}. Here, the large coordination number plays a key role to stabilize the classical magnetic orders, although the geometric and exchange frustrations coexist in the triangular lattice $J$-$K$-$\Gamma$ model. However, the SSF for the quantum phase in a small region around the point with $J=K=0$ and $\Gamma=1$ illustrated in Fig.~\ref{fig:StructureFactors}(h) exhibits high intensities at both $\tilde{\Gamma}$ and $\tilde{M}$ points, and it seems impossible for a classical magnetically ordering state to satisfy these two wave vectors simultaneously, so we infer that this quantum phase is a QSL candidate.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
    \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for a $12 \times 12$ cluster. (b) SSF corresponding to the spin configuration shown in (a). (c) Spin configuration obtained from the classical Monte Carlo calculations for a $24 \times 24$ cluster.}
\end{figure}

@@

Although the GSs of the pure Heisenberg, Kitaev and $\Gamma$ models are not QSL, the interplay of the Heisenberg, Kitaev and $\Gamma$ interactions may induce a possible QSL phase near the $\Gamma=1$ limit as discussed above according to the SSF. To have further understanding of the nature of this quantum phase that does not exist in the classical phase diagram~\cite{PhysRevB.92.165108}, we also calculate the DSF $A(\mathbf{k}, \omega)$, which in general can provide some critical information about the properties of a QSL. A typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}. We can find that a significant feature is that the whole spectrum is a broad continuum, which is a characteristic of QSL originating from the fractionalization of the $S=1$ spin excitations. Thus, the DSF gives another evidence that this quantum phase is a QSL. The DSF also shows another feature that the periodicity of its lower edge is doubled (i.e., $\tilde{M}$-$\tilde{\Gamma}$ forms a period instead of the usual $\tilde{M}$-$\tilde{M}$), which is a possible signature of the translational symmetry fractionalization of a $Z_{2}$ spin liquid~\cite{PhysRevB.90.121102,mei2015fractionalized,PhysRevB.99.205119}. Moreover, we also find that there is an obvious gap in the DSF. Thus, combined with all of the above results, we propose the GS of quantum $J$-$K$-$\Gamma$ model at the green area of the phase digram in Fig.~\ref{fig:QuantumPhaseDiagram} is a gapped $Z_{2}$ QSL.

@@

In summary, by using exact diagnoalization calculations and classical analyses, we map out the global phase diagram of the $J$-$K$-$\Gamma$ model. The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the positive $\Gamma$ point, for which we propose the ground state to be a gapped $Z_{2}$ QSL based on its spin excitation spectrum. We also provide detailed descriptions of the phase transition between the classical magnetic phases. On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ and antiferromagnetic Kitaev models have specific orders, although the classical analyses suggest that the GSs are highly degenerate.

>>>>

\title{Comprehensive study of the global phase diagram in the triangular $J$-$K$-$\Gamma$ model}

@@

\begin{abstract}
The celebrated Kitaev honeycomb model provides an analytically tractable example with an exact quantum spin liquid ground state. While in real materials, other types of interactions besides the Kitaev coupling ($K$) are present, such as the Heisenberg ($J$) and symmetric off-diagonal ($\Gamma$) terms, and these interactions can also be generalized to a triangular lattice. Here, we carry out a comprehensive study of the $J$-$K$-$\Gamma$ model on the triangular lattice covering the full parameters region, using the combination of the exact diagonalization, classical Monte Carlo and analytic methods, with an emphasis on the effects of the $\Gamma$ term. In the HK limit ($\Gamma=0$), we find five quantum phases which is quite similar to its classical counterpart. Among them, the stripe-A and dual N\'{e}el phase are robust against the introduction of the $\Gamma$-term, in particular the stripe-A extends to the region connecting the $K=-1$ and $K=1$ for $\Gamma<0$. Though the 120$^\circ$ N\'{e}el phase also extends to a finite $\Gamma$, its region has been largely reduced compared to the previous classical result. Interestingly, the ferromagnetic (dubbed as FM-A) phase and the stripe-B phase are unstable in response to an infinitesimal $\Gamma$ interaction. Moreover, we find five new phases for $\Gamma\ne 0$ which are elaborated by both the quantum and classic numerical methods. Part of the space previously identified as 120$^\circ$ N\'{e}el phase in the previous classical study is found to give way to the modulated stripe phase. Depending on the sign of the $\Gamma$ term, the FM-A phase is transited into the FM-B ($\Gamma>0$) and FM-C ($\Gamma<0$) phase with different spin orientations. Similarly, the stripe-B p hase is transited into the stripe-C ($\Gamma>0$) and stripe-A ($\Gamma<0$). Around the positive $\Gamma$ point, due to the interplay of the Heisenberg, Kiatev and $\Gamma$ interactions, we find a possible quantum spin liquid in a noticeable region with a continuum in spin excitations.

% Near the antiferromagetic Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism. Also, the order-by-disorder mechanism selects the ferromagnetic ordered states as the ground state out of the degenerate classical states for the pure $\Gamma$ models.We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit.
\end{abstract}

@@

In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED, the classical simulation and analytical analyses. In the HK limit ($\Gamma=0$), there are five classical phases: one FM, two stripe, one $120^{\circ}$ N\'{e}el and its dual phases. For the pure AFM Kitaev model, although the system has highly degenerate classical GSs composed of the stripe and nematic states, the order-by-disorder mechanism caused by quantum fluctuations makes the system select the stripe state to be the GS. When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases. With the aid of classical analysis, we determine the spin configuration for each magnetically ordered phase and explain why there are phase transitions between the phases with the same type of classical orders. On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate. For the possible QSL phase, based on the investigation of the spin excitation spectrum, we suggest the GS is a gapped $Z_{2}$ QSL.

@@

The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details). We find nine magnetically ordered phases and a phase ascribed to be a QSL. The nine ordered magnetic phases consist of three stripe phases (dubbed as stripe-A, strip-B and stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}), three ferromagnetic phases (dubbed as FM-A, FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}), one 120$^\circ$ N\'{e}el phase, one dual N\'{e}el phase and one modulated stripe phase. In the followings, we will discuss the details on the natures of these phases and the corresponding phase transitions.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/HKModel.pdf}
    \caption{\label{fig:HKModel}(Color online) Phase diagram in the HK limit ($\Gamma=0$). The double-arrow lines are the representative lines that connect the points exactly related by the FST.}
\end{figure}
Let's first discuss the HK limit for $\Gamma=0$. In accord with the previous study~\cite{KaiLi2015}, we find five quantum phases (see Fig.~\ref{fig:HKModel}). For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state (denoted as FM-A) for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively. As noted in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions. Thus, by virtue of the FST, we can identify other two magnetically ordered phases. For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$. Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state (denoted as stripe-A) of $\bm{S}$. Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$, and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$. Moreover, as indicated in Fig.~\ref{fig:HKModel}, the transition points $\beta=0.23\pi$ and $0.64\pi$ can also be well mapped to the transition points $\beta=1.90\pi$ and $1.82\pi$ through the FST. The isolated transition point $\beta=\pi$ is also consistent with the FST, as it is mapped to itself under the FST.

For the phase near the AFM Kitaev point ($J=\Gamma=0$, $K=1$), which is between $\beta=1.90\pi$ and $0.23\pi$,  the points in this phase are still mapped to those in the same phase under the FST, and it was supposed to be a magnetically disordered phase~\cite{KaiLi2015}. However, as shown in Fig.~\ref{fig:StructureFactors}(a), when we check the SSF in this phase, it is found that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase. We further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters. We find that there are two types of degenerate classical GSs, one of which has the stripe order and the other the nematic order, since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details). When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order. As shown in Fig.~\ref{fig:StructureFactors}(i), the peaks of SSF of the classical stripe orders are also consistent with the result calculated from ED [see Fig.~\ref{fig:StructureFactors}(a)]. Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-B. Moreover, every stripe order in this phase (see Appendix~\ref{apx:DegeneratedStates} for details) can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.

Then, let us study the effects of the $\Gamma$ term on the phase diagram. One may expect that the phases in the HK limit ($\Gamma=0$) would extend to a finite region in the global phase diagram of the $J$-$K$-$\Gamma$ model. Our ED results do show that the stripe-A phase can extend to a large region from $\Gamma>0$ to $\Gamma<0$, in particular it extends to the region connecting $K=-1$ to $K=1$ for $\Gamma<0$. The region of the dual N\'{e}el phase that was dubbed as a dual-$Z_{2}$ vortex crystal phase in Ref.~\onlinecite{PhysRevB.92.165108} also survives
the introduction of the $\Gamma$ term, though the region is much smaller than the stripe-A phase. These results
are consistent qualitatively with the classical results~\cite{PhysRevB.92.165108}. However, we find that an infinitesimal $\Gamma$ interaction can make the FM-A phase and the stripe-B phase unstable, so these two phases are actually phase boundaries in the global phase diagram. On the other hand, although the 120$^\circ$ N\'{e}el phase can also extend to a certain region, its area in the phase diagram is much smaller than the classical results~\cite{PhysRevB.92.165108}. Besides these phases that already exist in the HK limit, there are five other new phases according to our ED calculations. Since the SSF is a key physical quantity to reveal the nature of each quantum phases, especially the spin configuration of the ordered phases, we will discuss the properties of the phases with $\Gamma\neq0$ in detail according to the SSFs.

In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e. $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively. Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i). Thus, this further confirms that the stripe-A phase extents to a large region in the phase diagram. In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ for one of the new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.

@@

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the classical analyses by using the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, there are also several noncollinear magnetic orders energetically degenerate with the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). However, according to our ED calculations, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states. This selection of states among the degenerate classical ground states is the so called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) strip-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL. The green dashed lines marks the first BZ of the triangular lattice. (i) Characteristic wave vectors for the FM and stipe phases. See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
\end{figure}

According to the above analysis, we find that, unlike the case for the honeycomb lattice, the Kitaev interactions on the triangular lattice do not give rise to QSL states. Here, the large coordination number plays a key role to stabilize the classical magnetic orders, although the geometric and exchange frustrations coexist in the triangular lattice $J$-$K$-$\Gamma$ model. However, the SSF for the quantum phase in a small region around the point with $J=K=0$ and $\Gamma=1$ illustrated in Fig.~\ref{fig:StructureFactors}(h) exhibits high intensities at both $\tilde{\Gamma}$ and $\tilde{M}$ points, and it seems impossible for a classical magnetically ordering state to satisfy these two wave vectors simultaneously, so we infer that this quantum phase is a QSL candidate.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
    \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for $\alpha=0.3\pi$, $\beta=0.5\pi$ in a $12 \times 12$ cluster. (b) SSF corresponding to the spin configuration shown in (a). (c) Spin configuration obtained from the classical Monte Carlo calculations in a $24 \times 24$ cluster.}
\end{figure}

@@

Although the GSs of the pure Heisenberg, Kitaev and $\Gamma$ models are not QSL, the interplay of the Heisenberg, Kitaev and $\Gamma$ interactions may induce a possible QSL phase near the $\Gamma=1$ limit as discussed above according to the SSF. To have further understanding of the nature of this quantum phase that does not exist in the classical phase diagram~\cite{PhysRevB.92.165108}, we also calculate the DSF $A(\mathbf{k}, \omega)$, which in general can provide some critical information about the properties of a QSL. A typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}. We can find that a significant feature is that the whole spectrum is a broad continuum, which is a characteristic of QSL originating from the fractionalization of the $S=1$ spin excitations. Thus, the DSF gives another evidence that this quantum phase is a QSL. The DSF also shows another feature that the periodicity of its lower edge is doubled (i.e., $\tilde{M}$-$\tilde{\Gamma}$ forms a period instead of the usual $\tilde{M}$-$\tilde{M}$), which is a signature of the translational symmetry fractionalization of a $Z_{2}$ spin liquid~\cite{PhysRevB.90.121102,mei2015fractionalized,PhysRevB.99.205119}. Moreover, we also find that there is an obvious gap in the DSF. Thus, combined with all of the above results, we propose the GS of quantum $J$-$K$-$\Gamma$ model at the green area of the phase digram in Fig.~\ref{fig:QuantumPhaseDiagram} is a gapped $Z_{2}$ QSL.

@@

%In summary, by using exact diagnoalization calculations and classical analyses, we map out the global phase diagram of the $J$-$K$-$\Gamma$ model. The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the positive $\Gamma$ point, for which we propose the ground state to be a gapped $Z_{2}$ QSL based on its spin excitation spectrum. We also provide detailed descriptions of the phase transition between the classical magnetic phases. On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ and antiferromagnetic Kitaev models have specific orders, although the classical analyses suggest that the GSs are highly degenerate.

In summary, we carry out a comprehensive study of the $J$-$K$-$\Gamma$ model on a triangular lattice in the full parameter space and map out its global phase diagram by use of a combination of the exact diagonalization, the classical Monte Carlo simulation and analytical analyses. We find that there are five quantum phases in the limit of $\Gamma=0$. Among them, the 120$^\circ$ N\'{e}el, the dual N\'{e}el and one of the stripe phases extend into the region with $\Gamma\ne 0$. However, the other stripe and the ferromagnetic phases are unstable in response to an infinitesimal $\Gamma$ interaction. Due to the introduction of the $\Gamma$ term, five new phases emerge including two ferromagnetic phases, one stripe, one modulated stripe and a possible quantum spin liquid. We also elaborate that the pure $\Gamma$ model has a ferromagnetic ground state and the antiferromagnetic Kitaev model a stripe ground state, which are selected by the order-by-disorder mechanism from the degenerate classic ground states.
